Age-related changes in plant growth and traits

### 2017-05-05 Analysis-accessory.Rmd
small changes to accessory analysis from long ago

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)

@@

@@

>>>>

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b_predictions.png", height=2.5, width=7.3, units="in", res=300)

windowsFonts(
  Myriad=windowsFont("Myriad Pro")
)

par(mfrow=c(1,3), cex=1, omi=c(.1,.35,.05,.05), mai=c(.7,.5,.05,.15))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
#axis(2, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875,las=2)
#mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
#mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="seed count,",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,family="Myriad",cex=0.875)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
#axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
#mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
#mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,family="Myriad",cex=0.875)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
#axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
#mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
#mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="choosiness",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
mtext(text="pollen attraction costs,",side=1,line=0.3,family="Myriad",cex=0.875)
mtext(text="scaled to plant size",side=1,line=1.2,family="Myriad",cex=0.875)
mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,family="Myriad",cex=0.875)

@@

mod_seed$groupsummary$r2
mod_ovule$groupsummary$r2

@@

mod_choosy2$groupsummary$r2
